DS 5220 Project Proposal

### 2018-12-03 proposal/proposal2.Rmd
organize

Our team is basing our project idea on the "Quick, Draw!" Kaggle competition 
which classifies user drawings into one of 340 label categories. Drawings may 
be incomplete or not match the label. The challenge is to effectively build a 
recognizer that can work with this noisy data. The challenge is unique from an
algorithmic perspective because the data includes both time series and pattern
recognition components; areas that have traditionally used two different 
types of Neural Network Architectures. Our team uses a subset of the data to 
provide a solution to the Kaggle problem while taking a more in depth 
look at potential pitfalls and modeling strategy without having to use 
extensive computational resources.

@@

Google curated the Quick Draw Dataset as a collection of 50 million drawings
mapped to 345 categories. The drawings were submitted by players of the game
"Quick, Draw!" and captured as timestamped vectors, tagged with metadata such
as the requested drawing category and country code. The format of each drawing
array contains 3-dimensional vectors where components are the x,y coordinates
and time in milliseconds since the first point. We use a preprocessed version
of the dataset which is simplified and takes up about a tenth of the memory.
The simplified dataset contains a CSV file for each of the 345 categories.
Google was able to prepocess the data by performing the following steps: (1)
align each drawing to the top-left corner, (2) uniformly scale each drawing, 
(3) resample all strokes with a 1 pixel spacing, and (4) simplify all strokes
using the Ramer-Douglas-Peucker algorithm with an epsilon value of 2.0.

@@

We plan to use a Neural Network for this problem. The problem is unique in
that it has a time series component related to drawing stoke sequence, and
a image recognition component related the cumulative strokes. Recurrent Neural
Networks (RNN) are generally associated with time series. Convolutional Neural
Networks (CNN) are often associated with image recognition. The inclusion of
time series and pattern recognition components requires us to consider 
tradeoffs related to model accuracy, complexity, and algorithmic scalability.
For example, RNNs have been shown to be less scalable than CNNs due to
computational resource requirements. We have noted that researchers have
attempted to capture benefits of RNNs in CNNs through the use of techniques
such as dilation. We are still working through the best Neural Network 
Architecture for this problem.

>>>>

Our team is basing our project idea on the "Quick, Draw!" Kaggle competition 
which classifies user drawings into one of 345 label categories. Drawings may 
be incomplete or not match the label. The challenge is to effectively build a 
recognizer that can work with this noisy data. The challenge is unique from an
algorithmic perspective because the data includes both temporal and 
spatial components; areas that have traditionally used two different 
types of Neural Network Architectures. Our team attempts to provide a solution 
using a subset of the data, to the Kaggle problem, while taking a more in depth 
look at potential pitfalls and modeling strategy, without having to use 
extensive computational resources.

@@

Google curated the Quick Draw Dataset as a collection of 50 million drawings
mapped to 345 categories. The drawings were submitted by players of the game
"Quick, Draw!" and captured as timestamped vectors, tagged with metadata such
as the requested drawing category and country code. The format of each drawing
array contains 3-dimensional vectors of strokes, where components are the x,y 
coordinates and time in milliseconds since the first point. We use a preprocessed 
version of the dataset which is simplified and is about tenth the size.
The simplified dataset contains a CSV file for each of the 345 categories.
Google was able to prepocess the data by performing the following steps: (1)
align each drawing to the top-left corner, (2) uniformly scale each drawing, 
(3) resample all strokes with a 1 pixel spacing, and (4) simplify all strokes
using the Ramer-Douglas-Peucker algorithm with an epsilon value of 2.0.

@@

We plan to use Neural Networks for this problem. The problem is unique in
that it has a time series component related to drawing stroke sequences, and
an image recognition component related to the cumulative strokes. Recurrent Neural
Networks (RNN) are generally associated with time series. Convolutional Neural
Networks (CNN) are often associated with image recognition. The inclusion of
time series and pattern recognition components requires us to consider 
tradeoffs related to model accuracy, scalability, and algorithmic complexity.
For example, RNNs have been shown to be less scalable than CNNs due to
computational resource requirements. We have noted that researchers have
attempted to capture benefits of RNNs in CNNs through the use of techniques
such as dilation. The goal of this project is to compare the aforementioned
Neural Network Architectures, and present the findings.
